---
title: ""
page-layout: full
toc: false
anchor-sections: false
execute:
  freeze: auto
---

```{r setup}
#| include: false
source("R/site-stats.R")
source("R/home-helpers.R")
```

::: {.split-2-fullh}
<div class="scroll-hint"><span class="scroll-hint-label">Scroll</span><div class="scroll-hint-line"></div></div>
::: {}
[Interdisciplinarity + Data Science]{.label}

Researcher and data storyteller. 
I work at the intersection of social sustainability, climate and supply chains, and human rights — turning complex data into visuals that start the conversation.
Based at the University of Nottingham's Rights Lab.

::: {.tag-row}
[Sustainability]{.tag}
[Data Science]{.tag}
[Interdisciplinary studies]{.tag}
[Climate Change]{.tag}
[Industrial Ecology]{.tag}
[Complexity]{.tag}

:::

::: {.btn-row}
[Projects →](projects.html){.btn-primary}
[Portfolio](portfolio.html){.btn-outline}
:::
:::

::: {.coming-soon-panel}


::: {.h3}

:::

[Coming soon]{.tag}
:::

:::

::: {.split-3}

::: {.split-3-item}
::: {.section-num}
[Latest Publication]{.label} [01]{.label}
:::

::: {.h3}
[Current and recommended diets in the USA have embedded forced labour risk](publications.html)
:::

[Nature Food · 2025]{.body-sm}
:::

::: {.split-3-item}
::: {.section-num}
[Active Research]{.label} [02]{.label}
:::

::: {.h3}
[Climate Change, Decent Work and Workers Health: Vulnerabilities and Response in Brazilian Agriculture](projects.html)
:::

[Report · 2026]{.body-sm}
:::

::: {.split-3-item}
::: {.section-num}
[Data Visualisation]{.label} [03]{.label}
:::

::: {.h3}
[Climate–Decent Work Risk Assessment](portfolio.html)
:::

[Climate Risk Assessment · 2026 [Tableau]]{.body-sm}
:::

:::

<!-- ── ABOUT SUMMARY ────────────────────────────── -->

::: {.home-section}

::: {.page-band}
[02 — About]{.label}

::: {.h1}
Bridging disciplines, seeing the system
:::
:::

::: {.split-bio}

::: {}
Using quantitative methods, I draw on tools from engineering, ecology, and social science to follow goods and measure the hidden human cost.

::: {.tag-row}
[Supply chain mapping]{.tag}
[Life Cycle Assessment]{.tag}
[Climate modelling]{.tag}
[Data visualization]{.tag}
[Network analysis]{.tag}
:::


::: {.btn-row}
[Read more →](about.html){.btn-outline}
:::
:::

::: {}
```{r}
#| echo: false
#| results: asis
render_stats_strip()
```
:::

:::

:::

<!-- ── FEATURED PROJECTS ──────────────────────────── -->

::: {.home-section .subtle-bg}

::: {.page-band}
[03 — Projects]{.label}

::: {.h1}
Social sustainability, climate change and complex systems
:::
:::

::: {.home-cards}

```{r}
#| echo: false
#| results: asis
render_home_cards(get_featured_projects(n = 3))
```

:::

::: {.home-section-footer}
[All projects →](projects.html){.btn-primary}
:::

:::

<!-- ── FEATURED VISUALISATIONS ──────────────────────── -->

::: {.home-section}

::: {.page-band}
[04 — Portfolio]{.label}

::: {.h1}
Making invisible systems visible through data
:::
:::

::: {.home-cards}

```{r}
#| echo: false
#| results: asis
render_home_cards(get_featured_portfolio(n = 6))
```

:::

::: {.home-section-footer}
[All visualisations →](portfolio.html){.btn-primary}
:::

:::
